---
title: "Billfish Catch"
author: "Conner Smith"
date: "6/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(here)

```

## List of all Billfish stocks

BLKMARLINIO (Done)
BMARLINATL (Done)
BMARLINIO (Done)
BMARLINPAC (Done)
IPSAILIO (Done)
SAILEATL (Done)
SAILWATL (Done)
STMARLINIO (Done)
STMARLINNEPAC (Done)
STMARLINSWPO (Done)
STMARLINWCNPAC (Done)
SWORDEPAC (Done)
SWORDIO (Done)
SWORDMED (Done)
SWORDNATL (Done)
SWORDNPAC (Done)
SWORDSATL (Done)
SWORDSPAC (Not assessed)
SWORDWCNPAC (Done)
WMARLINATL (Done)

## BLKMARLINIO

```{r}
blkmarlinio_combined <- read_csv(here("data", "blkmarlinio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch) 
```

## BMARLINATL

```{r}
bmarlinatl_combined <- read_csv(here("data", "bmarlinatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

##BMARLINIO

```{r}
bmarlinio_combined <- read_csv(here("data", "bmarlinio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch) 
```

## BMARLINPAC 

```{r}
bmarlinpac_combined <- read_csv(here("data", "bmarlinpac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch)
```

## IPSAILIO

```{r}
ipsailio_combined <- read_csv(here("data", "ipsailio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch)
```

## SAILEATL

```{r}
saileatl_combined <- read_csv(here("data", "saileatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```


## SAILWATL

```{r}
sailwatl_combined <- read_csv(here("data", "sailwatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## STMARLINIO (no update)

```{r}
stmarlinio_combined <- read_csv(here("data", "stmarlinio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## STMARLINNEPAC

```{r}
stmarlinnepac_combined <- read_csv(here("data", "stmarlinnepac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## STMARLINSWPO

```{r}
stmarlinswpo_combined <- read_csv(here("data", "stmarlinswpo_catch.csv")) %>% 
  filter(year %in% c(1950:2020))
```

## STMARLINWCNPAC

```{r}
stmarlinwcnpac_combined <- read_csv(here("data", "stmarlinwcnpac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## SWORDEPAC

```{r}
swordepac_combined <- read_csv(here("data", "swordepac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## SWORDIO

```{r}
swordio_combined <- read_csv(here("data", "swordio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch)
```

## SWORDMED

```{r}
swordmed_combined <- read_csv(here("data", "swordmed_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## SWORDNATL

```{r}
swordnatl_combined <- read_csv(here("data", "swordnatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## SWORDSATL

```{r}
swordsatl_combined <- read_csv(here("data", "swordsatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## SWORDNPAC

```{r}
swordnpac_combined <- read_csv(here("data", "swordnpac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```


## SWORDSPAC (No assessmnet, not in RAM)

## SWORDWCNPAC

```{r}
swordwcnpac_combined <- read_csv(here("data", "swordwcnpac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch)
```

## WMARLINATL

```{r}
wmarlinatl_combined <- read_csv(here("data", "wmarlinatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```


## MASTER DF GOES HERE 

```{r}

# Run all chunks below before this 

bill_catch <- data.frame(blkmarlinio_combined) %>% 
  bind_rows(bmarlinatl_combined,
            bmarlinio_combined,
            bmarlinpac_combined,
            ipsailio_combined,
            saileatl_combined,
            sailwatl_combined,
            stmarlinio_combined,
            stmarlinnepac_combined,
            stmarlinswpo_combined,
            stmarlinwcnpac_combined,
            swordepac_combined,
            swordio_combined,
            swordmed_combined,
            swordnatl_combined,
            swordsatl_combined,
            swordnpac_combined,
            swordwcnpac_combined,
            wmarlinatl_combined)
  
```


## MASTER GRAPH GOES HERE

```{r}
ggplot(bill_catch, aes(x = year, y = catch, fill = stockid)) +
  geom_area() +
  labs(x = "Year", y = "Catch (metric tonnes)") +
  theme_minimal()
```