---
title: "Tuna Catch Graph"
author: "Conner Smith"
date: "6/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)

```

## List of all Tuna stocks 

ALBAIO 
ALBAMED (Done)
ALBANATL
ALBANPAC (Done)
ALBASATL
ALBASPAC (Done)
ATBTUNAEATL
ATBTUNAWATL
BIGEYEATL
BIGEYECWPAC
BIGEYEEPAC
BIGEYEIO
PACBTUNA
SBT (Done)
SKJCIO
SKJCWPAC
SKJEATL
SKJEPAC
SKJWATL
YFINATL
YFINCWPAC
YFINEIO
YFINEPAC

## MASTER DF GOES HERE 

```{r}
tuna_catch <- data.frame(sbt_combined) %>% 
  bind_rows(albamed_combined,
            albanpac_combined,
            albaspac_combined)
  
```


## MASTER GRAPH GOES HERE

```{r}
ggplot(tuna_catch, aes(x = year, y = catch, fill = stockid)) +
  geom_area() +
  labs(x = "Year", y = "Catch (metric tonnes)") +
  theme_minimal()
```


## SBT Catch (RAM + New)

```{r}

sbt_ram <- read_csv(here("data", "sbt_timeseries_2016.csv")) %>% 
  select(stockid, year, TCbest) %>% 
  rename(catch = TCbest)

# create dataframe of new catch values 
new_yr_sbt <- c(2017:2020)
new_tc_sbt <- c(13700,17100,16900,16441)

new_catch_sbt <- data.frame(new_yr_sbt, new_tc_sbt) %>%
  rename(year = new_yr_sbt,
         catch = new_tc_sbt) 

#Bind the new rows
sbt_combined <- bind_rows(sbt_ram, new_catch_sbt) %>% 
  filter(year %in% c(1950:2020)) %>% 
  replace_na(list(stockid = "SBT"))

# Now have SBT catch through 2020 

```

## ALBAMED Catch

```{r}
albamed_catch <- read_csv(here("data", "albamed_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(year, catch) 

albamed_stock_code <- c("ALBAMED")

albamed_combined <- cbind(albamed_stock_code, albamed_catch) %>% 
  rename(stockid = albamed_stock_code)
  
```

## ALBANPAC Catch

```{r}
albanpac_catch <- read_csv(here("data", "albanpac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(year, catch) 

albanpac_stock_code <- c("ALBANPAC")

albanpac_combined <- cbind(albanpac_stock_code, albanpac_catch) %>% 
  rename(stockid = albanpac_stock_code)
  
```

# ALBASPAC Catch

```{r}
albaspac_combined <- read_csv(here("data", "albaspac_catch.csv")) %>% 
  filter(year %in% c(1950:2020))
```

