---
title: "Shark Catch"
author: "Conner Smith"
date: "6/23/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(here)

```

## List of all Shark stocks

BLSHARIO (Done)
BLSHARNATL (Done)
BLSHARNPAC (Done)
BLSHARSATL (Done)
OWTSHARCWPAC (Questions on this one)
PORSHARNEATL (Done)
PORSHARNWATL (Done)
PORSHARSWATL (Catch inconsiderable/not in RAM)
SFMAKONATL (Done)
SFMAKONPAC (Done)
SFMAKONWPAC (Done)
SFMAKOSATL (Done)
SILSHARCWPAC (No catch/not in RAM)


## BLSHARIO

```{r}
blshario_combined <- read_csv(here("data", "shark", "blshario_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch) 
```

## BLSHARNATL

```{r}
blsharnatl_combined <- read_csv(here("data", "shark", "blsharnatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch)
```

## BLSHARSATL

```{r}
blsharsatl_combined <- read_csv(here("data", "shark", "blsharsatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch)
```

## BLSHARNPAC (only to 2012)

```{r}
blsharnpac_combined <- read_csv(here("data", "shark", "blsharnpac_timeseries_2012.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, TCbest) %>% 
  rename(catch = TCbest)
```

## PORSHARNEATL

```{r}
porsharneatl_combined <- read_csv(here("data", "shark", "porsharneatl_catch.csv")) %>%
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## PORSHARNWATL

```{r}
porsharnwatl_combined <- read_csv(here("data", "shark", "porsharnwatl_catch.csv")) %>%
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## PORSHARSWATL (Not in RAM, catch very small)

## SFMAKONATL (Not in RAM)

```{r}
sfmakonatl_combined <- read_csv(here("data", "shark", "sfmakonatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch)
```

## SFMAKOSATL (Not in RAM)

```{r}
sfmakosatl_combined <- read_csv(here("data", "shark", "sfmakosatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch)
```


## SFMAKONPAC

```{r}
sfmakonpac_combined <- read_csv(here("data", "shark", "sfmakonpac_catch.csv")) %>%
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch)
```


## SFMAKONWPAC

```{r}
sfmakonwpac_combined <- read_csv(here("data", "shark", "sfmakonwpac_timeseries_2003.csv")) %>%
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, TCbest) %>% 
  rename(catch = TCbest)
```

## SILSHARCWPAC (no catch)


```{r}

```


## MASTER DF GOES HERE 

```{r}

# Run all chunks below before this 

shark_catch <- data.frame(blshario_combined) %>% 
  bind_rows(blsharnatl_combined,
            blsharsatl_combined,
            blsharnpac_combined,
            porsharneatl_combined,
            porsharnwatl_combined,
            sfmakonatl_combined,
            sfmakosatl_combined,
            sfmakonpac_combined,
            sfmakonwpac_combined) %>% 
  filter(year %in% c(1975:2012))

shark_catch_top <- shark_catch %>% 
  group_by(stockid) %>% 
  summarize(catch_sum = sum(catch)) %>% 
  arrange(desc(catch_sum)) %>% 
  slice_max(catch_sum, n = 6)

top_stocks <- c(unique(shark_catch_top$stockid))
  
shark_catch_top6 <- shark_catch %>% 
  filter(stockid %in% top_stocks)
# Time series for only top 8 stocks 

shark_catch_other <- shark_catch %>% 
  filter(!stockid %in% top_stocks) %>% 
  group_by(year) %>% 
  summarize(catch = sum(catch)) %>% 
  mutate(stockid = "Other")
  
#Now all remaining stocks are "other"

shark_catch_condensed <- data.frame(shark_catch_top6) %>% 
  bind_rows(shark_catch_other) %>% 
  mutate(stock_name = case_when(stockid == "BLSHARIO" ~ "Blue Shark Ind.",
                                stockid == "BLSHARNATL" ~ "Blue Shark N. Atl.",
                                stockid == "BLSHARNPAC" ~ "Blue Shark N. Pac.",
                                stockid == "BLSHARSATL" ~ "Blue Shark S. Atl.",
                                stockid == "SFMAKONATL" ~ "SF Mako N. Atl.",
                                stockid == "SFMAKONPAC" ~ "SF Mako N. Pac.",
                                stockid == "Other" ~ "Other")) 
```


## MASTER GRAPH GOES HERE

```{r}
ggplot(shark_catch_condensed, aes(x = year, y = catch, fill = stock_name)) +
  geom_area() +
  labs(x = "Year", y = "Catch (metric tonnes)", fill = "Stock") +
  theme_minimal()
```