---
title: "Billfish Catch"
author: "Conner Smith"
date: "6/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)

```

## List of all Billfish stocks

BLKMARLINIO (Done)
BMARLINATL (Done)
BMARLINIO (Done)
BMARLINPAC (Done)
IPSAILIO (Done)
SAILEATL (Done)
SAILWATL (Done)
STMARLINIO (Done)
STMARLINNEPAC (Done)
STMARLINSWPO (Done)
STMARLINWCNPAC (Done)
SWORDEPAC
SWORDIO
SWORDMED
SWORDNATL
SWORDNPAC
SWORDSATL
SWORDSPAC
SWORDWCNPAC
WMARLINATL

## BLKMARLINIO

```{r}
blkmarlinio_combined <- read_csv(here("data", "blkmarlinio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch) 
```

## BMARLINATL

```{r}
bmarlinatl_combined <- read_csv(here("data", "bmarlinatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

##BMARLINIO

```{r}
bmarlinio_combined <- read_csv(here("data", "bmarlinio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch) 
```

## BMARLINPAC 

```{r}
bmarlinpac_combined <- read_csv(here("data", "bmarlinpac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch)
```

## IPSAILIO

```{r}
ipsailio_combined <- read_csv(here("data", "ipsailio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch)
```

## SAILEATL

```{r}
saileatl_combined <- read_csv(here("data", "saileatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```


## SAILWATL

```{r}
sailwatl_combined <- read_csv(here("data", "sailwatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## STMARLINIO (no update)

```{r}
stmarlinio_combined <- read_csv(here("data", "stmarlinio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## STMARLINNEPAC

```{r}
stmarlinnepac_combined <- read_csv(here("data", "stmarlinnepac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## STMARLINSWPO

```{r}
stmarlinswpo_combined <- read_csv(here("data", "stmarlinswpo_catch.csv")) %>% 
  filter(year %in% c(1950:2020))
```

## STMARLINWCNPAC

```{r}
stmarlinwcnpac_combined <- read_csv(here("data", "stmarlinwcnpac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```


## MASTER DF GOES HERE 

```{r}

# Run all chunks below before this 

bill_catch <- data.frame(blkmarlinio_combined) %>% 
  bind_rows(bmarlinatl_combined,
            bmarlinio_combined,
            bmarlinpac_combined,
            ipsailio_combined,
            saileatl_combined,
            sailwatl_combined,
            stmarlinio_combined,
            stmarlinnepac_combined,
            stmarlinswpo_combined,
            stmarlinwcnpac_combined)
  
```


## MASTER GRAPH GOES HERE

```{r}
ggplot(bill_catch, aes(x = year, y = catch, fill = stockid)) +
  geom_area() +
  labs(x = "Year", y = "Catch (metric tonnes)") +
  theme_minimal()
```