---
title: "Tuna Catch Graph"
author: "Conner Smith"
date: "6/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)

```

## List of all Tuna stocks 

ALBAIO (Done)
ALBAMED (Done)
ALBANATL (Done)
ALBANPAC (Done)
ALBASATL (Done)
ALBASPAC (Done)
ATBTUNAEATL (Done)
*ATBTUNAWATL (HOLD?)*
BIGEYEATL (Done)
BIGEYECWPAC (Done)
BIGEYEEPAC (Done)
BIGEYEIO (Done)
PACBTUNA (Done)
SBT (Done)
SKJCIO (Done)
SKJCWPAC (Done)
SKJEATL (NOT ASSESSED)
SKJEPAC (NOT ASSESSED)
SKJWATL (Done)
YFINATL
YFINCWPAC
YFINEIO
YFINEPAC


## SBT Catch (RAM + New)

```{r}

sbt_ram <- read_csv(here("data", "tuna", "sbt_timeseries_2016.csv")) %>% 
  select(stockid, year, TCbest) %>% 
  rename(catch = TCbest)

# create dataframe of new catch values 
new_yr_sbt <- c(2017:2020)
new_tc_sbt <- c(13700,17100,16900,16441)

new_catch_sbt <- data.frame(new_yr_sbt, new_tc_sbt) %>%
  rename(year = new_yr_sbt,
         catch = new_tc_sbt) 

#Bind the new rows
sbt_combined <- bind_rows(sbt_ram, new_catch_sbt) %>% 
  filter(year %in% c(1950:2020)) %>% 
  replace_na(list(stockid = "SBT"))

# Now have SBT catch through 2020 

```

## ALBAIO Catch

```{r}
albaio_catch <- read_csv(here("data", "tuna", "albaio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(year, catch) 

albaio_stock_code <- c("ALBAIO")

albaio_combined <- cbind(albaio_stock_code, albaio_catch) %>% 
  rename(stockid = albaio_stock_code)
```


## ALBAMED Catch

```{r}
albamed_catch <- read_csv(here("data", "tuna", "albamed_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(year, catch) 

albamed_stock_code <- c("ALBAMED")

albamed_combined <- cbind(albamed_stock_code, albamed_catch) %>% 
  rename(stockid = albamed_stock_code)
  
```

## ALBANATL (Ends in 2016)

```{r}
albanatl_combined <- read_csv(here("data", "tuna", "albanatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## ALBASATL (Ends in 2016)

```{r}
albasatl_combined <- read_csv(here("data", "tuna", "albasatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## ALBANPAC Catch

```{r}
albanpac_catch <- read_csv(here("data", "tuna", "albanpac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(year, catch) 

albanpac_stock_code <- c("ALBANPAC")

albanpac_combined <- cbind(albanpac_stock_code, albanpac_catch) %>% 
  rename(stockid = albanpac_stock_code)
  
```

# ALBASPAC Catch

```{r}
albaspac_combined <- read_csv(here("data", "tuna", "albaspac_catch.csv")) %>% 
  filter(year %in% c(1950:2020))
```

## ATBTUNAEATL

```{r}
atbtunaeatl_combined <- read_csv(here("data", "tuna", "atbtunaeatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## BIGEYEATL

```{r}
bigeyeatl_combined <- read_csv(here("data", "tuna", "bigeyeatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest)
```

## BIGEYECWPAC

```{r}
bigeyecwpac_combined <- read_csv(here("data", "tuna", "bigeyecwpac_catch.csv")) %>% 
  filter(year %in% c(1950:2020))
```
## BIGEYEEPAC (Ends in 2016)

```{r}
bigeyeepac_combined <- read_csv(here("data", "tuna", "bigeyeepac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest) 
```

## BIGEYEIO

```{r}
bigeyeio_combined <- read_csv(here("data", "tuna", "bigeyeio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch) 
```

## PACBTUNA

```{r}
pacbtuna_combined <- read_csv(here("data", "tuna", "pacbtuna_catch.csv")) %>% 
  filter(year %in% c(1950:2020))
```

## SKJCIO 

```{r}
skjcio_combined <- read_csv(here("data", "tuna", "skjcio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch) 
```

## SKJCWPAC

```{r}
skjcwpac_combined <- read_csv(here("data", "tuna", "skjcwpac_catch.csv")) %>% 
  filter(year %in% c(1950:2020))
```

## SKJEATL (NOT ASSESSED)

## SKJEPAC (NOT ASSESSED)

## SKJWATL

```{r}
skjwatl_combined <- read_csv(here("data", "tuna", "skjwatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest) 
```

## YFINATL

```{r}
yfinatl_combined <- read_csv(here("data", "tuna", "yfinatl_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest) 
```

## YFINCWPAC

```{r}
yfincwpac_combined <- read_csv(here("data", "tuna", "yfincwpac_catch.csv")) %>% 
  filter(year %in% c(1950:2020))
```


## YFINEIO

```{r}
yfineio_combined <- read_csv(here("data", "tuna", "yfineio_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  select(stockid, year, catch) 
```

## YFINEPAC

```{r}
yfinepac_combined <- read_csv(here("data", "tuna", "yfinepac_catch.csv")) %>% 
  filter(year %in% c(1950:2020)) %>% 
  rename(catch = TCbest) 
```


## MASTER DF GOES HERE 

```{r}

# Run all chunks below before this 

tuna_catch <- data.frame(sbt_combined) %>% 
  bind_rows(albaio_combined,
            albamed_combined,
            albanatl_combined,
            albasatl_combined,
            albanpac_combined,
            albaspac_combined,
            atbtunaeatl_combined,
            bigeyeatl_combined,
            bigeyecwpac_combined,
            bigeyeepac_combined,
            bigeyeio_combined,
            pacbtuna_combined,
            skjcio_combined,
            skjcwpac_combined,
            skjwatl_combined,
            yfinatl_combined,
            yfincwpac_combined,
            yfineio_combined,
            yfinepac_combined) %>% 
  filter(year %in% c(1950:2020))

tuna_catch_top <- tuna_catch %>% 
  group_by(stockid) %>% 
  summarize(catch_sum = sum(catch)) %>% 
  arrange(desc(catch_sum)) %>% 
  slice_max(catch_sum, n = 8)

top_stocks <- c(unique(tuna_catch_top$stockid))
  
tuna_catch_top8 <- tuna_catch %>% 
  filter(stockid %in% top_stocks)
# Time series for only top 8 stocks 

tuna_catch_other <- tuna_catch %>% 
  filter(!stockid %in% top_stocks) %>% 
  group_by(year) %>% 
  summarize(catch = sum(catch)) %>% 
  mutate(stockid = "Other")
  
#Now all remaining stocks are "other"

tuna_catch_condensed <- data.frame(tuna_catch_top8) %>% 
  bind_rows(tuna_catch_other)
  
```


## MASTER GRAPH GOES HERE

```{r}
ggplot(tuna_catch_condensed, aes(x = year, y = catch, fill = stockid)) +
  geom_area() +
  labs(x = "Year", y = "Catch (metric tonnes)") +
  theme_minimal()
```